\section{Extra}
\subsection{Vim Settings}

Create \code{~/.vimrc}.

In order to permanently have numbering in vim/vi/vimdiff, add \code{:set number} into \code{.vimrc}.

\subsection{Change keyboard layout - MicroSoft Keyboard Layout Creator (MSKLC)}
Download MicroSoft Keyboard Layout Creator (MSKLC):\\
\url{https://www.microsoft.com/en-us/download/details.aspx?id=102134}

Extract the files and run the installation. If the installation says that \tttbf{.NET Framework} has to be installed, then follow the instructions below.

\begin{enumerate}
    \item Press \tttbf{Windows + R}.Run \tttbf{appwiz.cpl}.
    
    \item Click \tttbf{'Turn Windows features on or off'}.
    
    \item Enable \tttbf{.NET Framework 3.5 (includes .NET 2.0 and 3.0)}.
    
    \item Follow the on-screen instructions and let Windows install the necessary files.
    
    \item Now try to install \tttbf{MSKLC} again.
\end{enumerate}

Now run \tttbf{Microsoft Keyboard Layout Creator ...}.

\begin{enumerate}
    \item Click \tttbf{File\ra Load Existing Keyboard} and pick the keyboard which the computer have e.g. \tttbf{Swedish}
    
    \item Now save a backup by clicking \tttbf{File\ra Save Source File As...}.
    
    \item Now change the name of the current keyboard to avoid saving on the backup after doing the changes. Click \tttbf{Project\ra Properties} and change the name etc. as before but to another name such as \texttt{Custom}.
    
    \item Now, do the changes to the keyboard layout as you which.
    \begin{itemize}
        \item \{ mapped to \texttt{AltGr + A}
        
        \item {[} mapped to \texttt{AltGr + S}
        
        \item {]} mapped to \texttt{AltGr + D}
        
        \item \} mapped to \texttt{AltGr + F}
        
        \item \textbackslash\ mapped to \texttt{AltGr + G}
    \end{itemize}
    
    \item Run the validation by clicking \tttbf{Project\ra Validate Layout} and watch for errors. The warnings can usually be ignored.
    
    \item Test write with the layout by clicking \tttbf{Project\ra Test Keyboard Layout}.
    
    \item Create the necessary files for the final keyboard layout by clicking \tttbf{Project\ra Build DLL and Setup Package}. When asked about opening the directory where the files were created, click \tttbf{Yes}. Usually created in \tttbf{...\textbackslash Documents}.
    
    \item Run the \tttbf{setup} file and restart the computer.
\end{enumerate}

\subsection{Windows code compare program - Meld}
Comparing and inserting code. Great when someone sends you a changed file and might want to integrate it into yours.
\url{https://meldmerge.org/}